---
title: "Unit_tests"
output: html_document
date: "2024-04-18"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load necessary libraries and packages
```{r cars}

library(ggplot2)
library(data.table)
library(tidyverse)
library(dplyr)
library("ggpubr")
library(rgl)
library("spatstat.geom") 
library(plotly)
#install.packages("scatterplot3d") # Install
library("scatterplot3d") # load
install.packages("collapse")
library(reshape2)
library(Matrix)
library(gtools) 
library(abind)


xDim=200
yDim=200
diploid<-c(2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2,2)


```



 Spatial- and Karyotype-distance analysis:  cell-to-cell  at one time point
 1.Input data contains cell locations and corresponding karyotype in the form (x,y c1,c2,c3,...,c22) collected at the final time point

```{r pressure, echo=FALSE}

cellKaryotypeData<-as.matrix(read.csv("/Users/john/Documents/IMO/ploidy_abm/output/200-karyotype_Location.csv",header=FALSE))
#Isolate all locations with no cells
m=c()
for(i in 1:nrow(cellKaryotypeData)){
  #if both x and y coordinates are zero, then there is no cell there, remove
  if(cellKaryotypeData[i,1]==0 && cellKaryotypeData[i,2]==0){
    #Collect zero indexes
    m<-c(m,i)
  }
}
#Remove zero indexed rows (without a cell)
cellKaryotypeData<-cellKaryotypeData[-m,]
columnNames<-c("x","y","C1","C2","C3","C4","C5","C6","C7","C8","C9","C10",
               "C11","C12","C13","C14","C15","C16","C17","C18","C19","C20","C21","C22")
colnames(cellKaryotypeData)<- columnNames

#Select a subset of data (Size is too large)
index<-seq(1,nrow(cellKaryotypeData),4)
cellKaryotypeData<-cellKaryotypeData[index,]

manhattanDistance <- function(vect1, vect2){
  dist <- abs(vect1 - vect2)
  dist <- sum(dist)
  return(dist)
}


#Represent data as a n-by-2 matrix whose 1st column contains PAIRWISE spatial dts and 2nd column has corresponding  karyotype dist btn cells

spatialDistBtnCells<-dist(cellKaryotypeData[,1:2], method = "euclidean", diag = FALSE, upper = FALSE)
karyotypeDistBtnCells<-dist(cellKaryotypeData[,3:24], method = "manhattan", diag = FALSE, upper = FALSE)

paired_distances<-t(rbind(c(spatialDistBtnCells),c(karyotypeDistBtnCells)))




paired_distances_DF<-data.frame(paired_distances)
col<-c("spatial_dts","karyotype_dts")
colnames(paired_distances_DF)<-col

#Aggregate over spatial dist
z1 <- aggregate(list(karyotype_dts=paired_distances_DF$karyotype_dts),
                by=list(spatial_dts=paired_distances_DF$spatial_dts),
                mean)


z2 <- aggregate(list(karyotype_dts=paired_distances_DF$karyotype_dts),
                by=list(spatial_dts=paired_distances_DF$spatial_dts),
                function(q){
                  mean(q==0)
                })



correlation<-round(cor(z1$spatial_dts,z1$karyotype_dts),3)
cor_coef<-paste("r =",correlation)

p1 <- ggplot(z1,aes(x=spatial_dts))+
  geom_point(mapping=aes(y=karyotype_dts,color="Karyo dts"))+
  geom_vline(xintercept=(+10),color="blue",lty=2)+
  #geom_text(aes(x=62,y=1.7,label=paste("r =",correlation)))+
  labs(x="Spatial distance",y="Mean karyotype dist.",title=paste("Cell-to-cell: Spatial distance vs karyotype distance, t=200\n "  ,"(",cor_coef,")"))

p1


dist_under10<-z1[z1$spatial_dts<10,]
cor_coef10<-paste("r =",round(cor(dist_under10$spatial_dts,dist_under10$karyotype_dts),3))

p2<-ggplot(dist_under10,aes(x=spatial_dts))+
  geom_point(mapping=aes(y=karyotype_dts,color="Karyo dts"))+
  geom_vline(xintercept=(+10),color="blue",lty=2)+
  geom_smooth(aes(y=karyotype_dts))+
  labs(x="Spatial distance (Under 10)",y="Mean karyotype dist.",title=paste("Cell-to-cell: Spatial distance vs karyotype distance, t=200 \n "  ,"(",cor_coef10,")"))

p2+theme(text=element_text(size=12))

p3 <- ggplot(z2,aes(x=spatial_dts))+
  geom_point(mapping=aes(y=karyotype_dts,color="Karyo dts"))+
  geom_vline(xintercept=(+10),color="blue",lty=2)+
  #geom_text(aes(x=62,y=1.7,label=paste("r =",correlation)))+
  labs(x="Spatial distance",y="prob. that karyotypes x-dist apart are identical",title="Fraction of  karyotypes  identical at a given spatial dist "  )

p3

g<-ggarrange(p1,p2,p3,nrow=2,ncol=2)
annotate_figure(g, top = text_grob("Cell-to-cell: Spatial dist. vs karyotype dist.", 
                                   color = "blue", face = "bold", size = 14))

```


Response to spatial-karyotype distance correlation to mis-segregation

```{r}

#Correlation values from  simulations with different mis-segregation rates are recorded for real data and random data initialization
cor_randomData<- c(0,0.617,0.36,0.43,0.684,0.716,0.72,0.733,0.723,0.739)
cor_realData <- c(0.978,0.983,0.98,0.982,0.975,0.972,0.963,0.949,0.942,0.94)
mis_rate<-c(0,0.001,0.0015,0.0025,0.05,0.1,0.2,0.3,0.4,0.5)

cor_df<-data.frame(mis_rate)
cor_df$realData<-cor_realData
cor_df$randomData<-cor_randomData

b<-ggplot(cor_df,aes(x=mis_rate))+
  geom_point(mapping=aes(y=realData,color="realData"),size=3)+
  geom_smooth(mapping=aes(y=realData,color="realData"))+
  geom_point(mapping=aes(y=randomData,color="randomData"),size=3)+
  geom_smooth(mapping=aes(y=randomData,color="randomData"),method=NULL,se=FALSE)+
  labs(x="Mis-segregation Rate",y="Correlation coefficient",title=paste("Mis_rate against Space-karyotype dist. correlation"))+
  theme(text=element_text(size=14))
b


```




The next chunk analyses Spatial- and Karyotypic-distances  spot-wise




```{r}

Space_karyo_Data<-as.matrix(read.csv("/Users/john/Documents/IMO/ploidy_abm/100_Spatial_karyo_dts.csv",header=FALSE)) # data
Space_karyo_Data<-matrix(as.numeric(Space_karyo_Data[-1,]),ncol=3)

columnNames<-c("Distance_btn_regions","Avg_dts_btn_spots","Max_Karyotype_dts")
colnames(Space_karyo_Data)<-columnNames
Space_karyo_DF<-data.frame(Space_karyo_Data)

#remove rows with N/A data
Space_karyo_DF<-Space_karyo_DF[!is.na(Space_karyo_DF$Avg_dts_btn_spots),]


Space_karyo_DF<-aggregate(list(Max_Karyotype_dts=Space_karyo_DF$Max_Karyotype_dts),
                         by=list(Avg_dts_btn_spots=Space_karyo_DF$Avg_dts_btn_spots),
                         mean)



Space_karyo_DF<-Space_karyo_DF[Space_karyo_DF$Avg_dts_btn_spots<75,]

ggplot(Space_karyo_DF, aes(x=Avg_dts_btn_spots)) +
  geom_point(mapping=aes(y=Max_Karyotype_dts,colour="Max Karyo dts"),size=2)+
  labs(x="Distance between spots", y="Max. Karyotype between spotes",title="Spotwise comparison: Initialized with data, t_n=500")


cor(Space_karyo_DF$Avg_dts_btn_spots,Space_karyo_DF$Max_Karyotype_dts)

r12<-Space_karyo_DF

rdf<-r12
rdf$Avg_dts_btn_spots<-mean(r12$Avg_dts_btn_spots,r12$Avg_dts_btn_spots,r12$Avg_dts_btn_spots)
rdf$Max_Karyotype_dts<-mean(r12$Avg_dts_btn_spots)



ggplot(r12, aes(x=Avg_dts_btn_spots)) +
  geom_point(mapping=aes(y=Max_Karyotype_dts,colour="Max Karyo dts"))+
  geom_smooth(aes(y=Max_Karyotype_dts),method = "lm", se = FALSE)+
  #geom_line(aes(y=Max_Karyotype_dts))+
  labs(x="Distance between spots", y="Max. Karyotype between spotes",title="Spotwise comparison: Initialized with real data, t_n=100")
```


 Vessel distance  vs density and diversity analysis
 Spots are selected and  the density, diversity and distance from nearest  vessel data is collected from each spot
 
 
```{r}
setwd("/Users/john/Documents/IMO/ploidy_abm")
DistanceDensityData<-as.matrix(read.csv("/Users/john/Documents/IMO/ploidy_abm/100_DistanceDensity.csv",header=FALSE))
DistanceDensityData<-matrix(as.numeric(DistanceDensityData[-1,]),ncol=6) 



sites<-seq(1,nrow(DistanceDensityData))
DistanceDensityData<-cbind(sites,DistanceDensityData)


columnNames<-c("Site","x","y","Avg_spatial_Dist","Density","Diversity","Avg_Karyotype_Dist")
colnames(DistanceDensityData)<-columnNames

DistanceDensity_DF<-as.data.frame(DistanceDensityData)
  
DistanceDensity_DF<-DistanceDensity_DF[!is.na(DistanceDensity_DF$Avg_spatial_Dist),] #remove rows with N/A  measurements                             
                         

ggplot(DistanceDensity_DF, aes(x=Avg_spatial_Dist)) +
  geom_smooth(mapping=aes(y=Density,colour="Density"),method=lm, se=FALSE)+
  geom_point(mapping=aes(y=Density,colour="Density"))+
  #geom_smooth(aes(y=Density,colour="Density"),method=lm, se=FALSE)+
  #geom_smooth(mapping=aes(y=Diversity,colour="Diversity")+
  geom_point(mapping=aes(y=Diversity,colour="Diversity"))+
  geom_smooth(aes(y=Diversity,color="Diversity"),method=lm, se=FALSE)+
  labs(x="Distance from vessel", y="Cell Density/Diversity",title="Distance vs density/Diversity: Real data, t_n=100 ")  

```
 
 
 Spatial Autocorrelation: This test the spatial relatedness of karyotype distribution
 Hytpothesis is that spatial close clones are also genetically close
 
 
```{r}

  library(sp)
  library(spdep)
  #Set working direction to load data from
  setwd("/Users/john/Documents/IMO/ploidy_abm/output")
  
SAData<-as.matrix(read.csv("/Users/john/Documents/IMO/ploidy_abm/output/200-karyotype_Location.csv",header=FALSE))

#remove empty locations
m=c()
for(i in 1:nrow(SAData)){
  #if both x and y coordinates are zero, then there is no cell there, remove
  if(SAData[i,1]==0 && SAData[i,2]==0){
    #Collect zero indexes
    m<-c(m,i)
  }
}
  SAData<-SAData[-m,]
  
#Extract unique karyotypes in the data
  UniqueKaryotype<-unique(SAData[,3:24])
  unique_index<-seq(1,nrow(UniqueKaryotype))
  UniqueKaryotype<-cbind(unique_index,UniqueKaryotype) #assign unique index to each unique karyotype

  featureData<-matrix(nrow=nrow(SAData),ncol=3)# holds cell location (x,y) and unique attribute (karyotype identifier)
  featureData[,1:2]<-SAData[,1:2]
  
  for(k in 1:nrow(SAData)){
    for(j in 1:nrow(UniqueKaryotype)){
      if(identical(SAData[k,3:24],UniqueKaryotype[j,2:23])){
        featureData[k,3]<-UniqueKaryotype[j,1]
        break
      }
    }
  }
  
df<-data.frame(featureData)
  
ggplot(df, aes(x = X1,y=X2))+
  geom_point(aes(color=X3))+
  labs(x="xDim",y="yDim")

#set longitude and latittude values for define=ing polygons







# Define the coordinates for each point (x, y)
points <- cbind(df$X1, df$X2)  # Example coordinates

# Create a list to store Polygons objects
polygons <- vector("list", length = nrow(points))

# Create Polygons objects for each point
for (i in 1:nrow(points)) {
  point <- points[i, ]
  polygon <- Polygons(list(Polygon(matrix(point, nrow = 1))), ID = as.character(i))
  polygons[[i]] <- polygon
}

# Create a SpatialPolygons object from the list of Polygons objects
spatial_polygons <- SpatialPolygons(polygons)

# Plot the polygons
#plot(spatial_polygons, col = rainbow(nrow(points)), main = "Polygons with Single Points")

plot(spatial_polygons, border = "red", lwd = 2, main = "Edges of Polygons Defined by Single Points/cell locations")

#Fill inside of polygons
for(i in 1:nrow(points)){
  points(points[i,1], points[i,2], col = "purple", pch = 20)  # Plot the single point
}



#Adding the desired attribute
spatial_polygons$karyo<-df$X3

#spatial_polygons<-df
# Define a distance threshold for neighbors
distance_threshold <- 1 

# Compute neighbors based on distance
nb <- knn2nb(knearneigh(coordinates(spatial_polygons), k = 1))

# Adjust neighbors based on distance threshold
nb <- dnearneigh(coordinates(spatial_polygons), 0, distance_threshold)

# Construct spatial weights matrix
w <- nb2listw(nb, style = "B")

# Perform Moran's test (example)
# Assuming you have a variable 'karyo' associated with each point

moran_result <- moran.test(spatial_polygons$karyo, listw = w)

# View the Moran's test results
print(moran_result)

#Extract the spatially lagged values for each region
spatial_polygons$lag <- lag.listw(w, spatial_polygons$karyo)

#Plot lagged values against karyotype numbers
M <- lm(lag ~ karyo, spatial_polygons)

plot( lag ~ karyo, spatial_polygons, xlim=c(-5,200),pch=21, las=1,  col = "grey40", bg="grey80",
      main="Attribute: Karyotype vs spatially Lagged values",xlab="Karyotype",ylab="spatially lagged values")
 abline(M, col="blue",lwd=3) # Add the regression line from model M
 abline(v = mean(spatial_polygons$karyo), lty=5, col = "green")
 abline(h = mean(spatial_polygons$karyo), lty=5, col = "red")
 legend(150, 500, legend=c("Reg", "Mean karyotype"),
        col=c("blue", "red"), lty=1:2, cex=0.7)
 
 #Computing Moran's coefficient
 moran(spatial_polygons$karyo, listw = w, n = length(nb), S0 = Szero(w))
 
 #Test for significance : Monte carlo 
 MC<- moran.mc(spatial_polygons$karyo, w, nsim = 999)
 MC
 plot(MC,col="red",main="",xlab="Karyotype",las=1)
 
 
```
 
